The Name of the Title Is Hope

### 2025-01-29 paper.tex
#7 added another thought

\subsubsection{Decoupled-Fallback}
\thomas{Given that "lock" has an extensive history of use in computer science and this is not that kind of lock, perhaps a better choice of phrase would be better. I've decided to refer to it as a "control flag"} \john{Good idea. ``Status flag'', perhaps?}
Prior to kernel launch, all tiles in the spine are initialized to the \emph{Not Ready} state. During partition index acquisition, we also initialize a shared memory \emph{control flag} to facilitate synchronization within the workgroup during the \emph{Decoupled-Fallback} phase. This flag governs both the initiation of fallback operations and the entry and exit of the entire phase, which begins immediately after the workgroup-wide scan over partial reductions is completed.
\john{Maybe a sentence that describes the state progression at a high level? e.g., ``the state of each workgroup begins at INVALID, moves to READY, then to INCLUSIVE, the state never moves backwards, each workgroup can operate independently and change its own state and also, during lookback, the state of preceding workgroups'', that sort of thing.}
\john{I might also say something like ``in the following discussion, we assume the `add' monoid and use terms like `add' and `sum', but the algorithm works with any monoid''. That gets rid of awkward terms like ``accumulate''. I don't feel strongly about this.}
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{graphics/FlowChart.pdf}
  \caption{Decoupled-Fallback}
\end{figure}
\begin{enumerate}
  \item[(0)] \textbf{Posting Local Reduction:} Each workgroup posts its local reduction---the result of the workgroup-wide scan over partials---to global memory and updates its tile state to \emph{Ready}. If it is the first work tile, its local reduction \emph{is} its inclusive reduction. In this case, the workgroup updates its tile state directly to \emph{Inclusive} and bypasses the lookback entirely.

>>>>

\subsubsection{Decoupled-Fallback}
\thomas{Given that "lock" has an extensive history of use in computer science and this is not that kind of lock, perhaps a better choice of phrase would be better. I've decided to refer to it as a "control flag"} \john{Good idea. ``Status flag'', perhaps?}
Prior to kernel launch, all tiles in the spine are initialized to the \emph{Not Ready} state. During partition index acquisition, we also initialize a shared memory \emph{control flag} to facilitate synchronization within the workgroup during the \emph{Decoupled-Fallback} phase. This flag governs both the initiation of fallback operations and the entry and exit of the entire phase, which begins immediately after the workgroup-wide scan over partial reductions is completed.
\john{Maybe a sentence that describes the state progression at a high level? e.g., ``the state of each workgroup begins at INVALID, moves to READY, then to INCLUSIVE, the state never moves backwards, each workgroup can operate independently and change its own state and also, during lookback, the state of preceding workgroups'', that sort of thing. Also, we present the algorithm from the perspective of one workgroup, which at all times has a pointer to a ``current tile'' on which it is working. (Sloppily worded, sorry.)}
\john{I might also say something like ``in the following discussion, we assume the `add' monoid and use terms like `add' and `sum', but the algorithm works with any monoid''. That gets rid of awkward terms like ``accumulate''. I don't feel strongly about this.}
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{graphics/FlowChart.pdf}
  \caption{Decoupled-Fallback}
\end{figure}
\begin{enumerate}
  \item[(0)] \textbf{Posting Local Reduction:} Each workgroup posts its local reduction---the result of the workgroup-wide scan over partials---to global memory and updates its tile state to \emph{Ready}. If it is the first work tile, its local reduction \emph{is} its inclusive reduction. In this case, the workgroup updates its tile state directly to \emph{Inclusive} and bypasses the lookback entirely.
